\cvsection{Work Experience}

\begin{cventries}

\cventry
{University of Twente} % Job title
{Teaching Assistant (TA, Student Assistent)} % Organization
{Enschede, Netherlands} % Location
{2016 - Present} % Date(s)
{ 
\begin{cvitems} % Description(s) of tasks/responsibilities
     	\item Teaching Assistant for the Bachelor Technical Computer Science courses.
     	\item TA during the following modules. Modules are comprised of multiple courses following a general topic. 
     	\begin{itemize}
     		\item Pearls of Computer Science (2016/2017, 2017/2018, 2018/2019, 2019/2020). An introduction to Computer Science.
     		\item Software Systems (2017/2018, 2018/2019, 2019/2020). Introduction to designing, implementing and testing software.
     		\item Network Systems (2017/2018, 2018/2019). A module with courses on computer networking.
     		\item Data \& Information (2017/2018, 2018/2019). A module with courses on structured/unstructured data, databases, scripting frameworks and services such as RESTful services.
     	\end{itemize}
\end{cvitems}
}

\cventry
{University of Twente} % Job title
{Developer Quizzard} % Organization
{Enschede, Netherlands} % Location
{Feb. 2017 - May 2019} % Date(s)
{
	\begin{cvitems}
		\item Quizzard: A teaching quiz application.
		\item Mainly back end development. 
		\item Technologies used: Java, Maven, PostgreSQL, Spring Boot, Thymeleaf, Hibernate, React.
		\item GitLab page: \url{https://git.tworem.nl/tnb/quizzard}
	\end{cvitems}
}

\cventry
{University of Twente} % Job title
{Back end developer Groufty} % Organization
{Enschede, Netherlands} % Location
{Feb. 2016 - June 2016} % Date(s)
{
  \begin{cvitems}
	\item Groufty: group peer review system.
	\item Technologies used: Java, Maven, PostgreSQL, Spring Boot, Thymeleaf, Hibernate.
	\item GitHub page: \url{https://github.com/utwente/Groufty}
  \end{cvitems}
}


\end{cventries}
