\cvsection{Publications}

\begin{cventries}
	
	
	\cventry
	{TACAS 2022} % Degree
	{Alpinist: an Annotation-Aware GPU Program} % Institution
	{ Munich, Germany} % Location
	{April 2–7, 2022} % Date(s)
	{
		\begin{cvitems} % Description(s) bullet points
			\item Authors: \"Omer \c{S}akar, Mohsen Safari, Marieke Huisman, Anton Wijs
			\item Abstract: Over the last years, deductive program verifiers have substantially improved, and their applicability on non-trivial applications has been demonstrated. However, a major bottleneck is that for every new programming language, a new deductive verifier has to be built. This paper describes the first steps in a project that aims to address this problem, by language-agnostic support for deductive verification: Rather than building a deductive program verifier for every programming language, we develop deductive program verification technology for a widely-used intermediate representation language (LLVM IR), such that we eventually get verification support for any language that can be compiled into the LLVM IR format. Concretely, this paper describes the design of VCLLVM, a prototype tool that adds LLVM IR as a supported language to the VerCors verifier. We discuss the challenges that have to be addressed to develop verification support for such a low-level language. Moreover, we also sketch how we envisage to build verification support for any specified source program that can be compiled into LLVM IR on top of VCLLVM.
			\item DOI: \href{https://doi.org/10.1007/978-3-030-99527-0_18}{10.1007/978-3-030-99527-0\_18}
\			
		\end{cvitems}
	}
	
		\cventry
	{FASE 2024} % Degree
	{First Steps towards Deductive Verification of LLVM IR} % Institution
	{Luxembourg City, Luxembourg} % Location
	{April 8–11, 2024} % Date(s)
	{
		\begin{cvitems} % Description(s) bullet points
			\item Authors: Dré van Oorschot, Marieke Huisman, \"Omer \c{S}akar
			\item Abstract: Over the last years, deductive program verifiers have substantially improved, and their applicability on non-trivial applications has been demonstrated. However, a major bottleneck is that for every new programming language, a new deductive verifier has to be built. This paper describes the first steps in a project that aims to address this problem, by language-agnostic support for deductive verification: Rather than building a deductive program verifier for every programming language, we develop deductive program verification technology for a widely-used intermediate representation language (LLVM IR), such that we eventually get verification support for any language that can be compiled into the LLVM IR format. Concretely, this paper describes the design of VCLLVM, a prototype tool that adds LLVM IR as a supported language to the VerCors verifier. We discuss the challenges that have to be addressed to develop verification support for such a low-level language. Moreover, we also sketch how we envisage to build verification support for any specified source program that can be compiled into LLVM IR on top of VCLLVM.
			\item DOI: \href{https://doi.org/10.1007/978-3-031-57259-3_15}{10.1007/978-3-031-57259-3\_15}
		\end{cvitems}
	}
	

\end{cventries}
